---
title: "Device Type Prediction"
author: "Nada Hossam"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    keep_md: yes
  pdf_document: default
  word_document: default
---



# Executive Summary

The main goal is to 


# Loading the Data


```{r}

library(caret)
library(kernlab)

trainData <- read.csv("E:/Nada/Others/Courses/Data Science Specialization/Ex/Course 8/pml-training.csv", sep = ",")

testData <- read.csv("E:/Nada/Others/Courses/Data Science Specialization/Ex/Course 8/pml-testing.csv", sep = ",")

table(trainData$classe)

```

The graph displays the mpg with respect to the type of car (automatic / manual)

```{r}

mdlda <- train(classe ~ ., data = trainData, method = "lda", na.action = na.pass)
plda <- predict(mdlda, testData)
plda

mdnb <- train(classe ~ ., data = trainData, method = "nb", na.action = na.pass)
pnb <- predict(mdnb, testData)
pnb

```



# Data Analysis


## Student's t-test 

```{r}

#library(datasets)

#mdlda <- train(Species ~ ., data = iris, method = "lda")
#plda <- predict(mdlda, iris)
#plda

#mdnb <- train(Species ~ ., data = iris, method = "nb")
#pnb <- predict(mdnb, iris)
#pnb


```


## Regression Model

```{r}



```


## Multivariate Model

```{r}



```



# Results


## Is an automatic or manual transmission better for MPG?

Manual transmission is better for mpg.


## The MPG difference between automatic and manual transmissions

Cars with manual transmissions have 2.94 more mpg compared to automatic ones.


